---
title: "Replicating UN Security Council Voting"
author: "Arthur Tartee"
date: "2023-05-08"
output: html_document
---

## Installationi

You can install and load the following packages here or as you go along. I will point out in my code chunk when each will be needed:

```{r setup, eval = FALSE, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(magrittr)
library(tidyverse)
library(patchwork)
library(scales)
library(showtext)
library(extrafont)
install.packages("unvotes")
```

You can also download the dataset from [here](https://dataverse.harvard.edu/dataset.xhtml?persistentId=hdl:1902.1/12379):

Erik Voeten "Data and Analyses of Voting in the UN General Assembly" Routledge Handbook of International Organization, edited by Bob Reinalda (published May 27, 2013)


## Datasets

The package contains three datasets and you will need to load tidyverse here. First is the history of each country's vote. These are represented in the `un_votes` dataset, with one row for each country/vote pair:

```{r, include=TRUE}
library(tidyverse)
library(unvotes)

un_votes
```

The package also contains a dataset of information about each roll call vote, including the date, description, and relevant resolution that was voted on:

```{r}
un_roll_calls
```

Finally, the `un_roll_call_issues` dataset shows relationships betwen each vote and six issues - Arms control and disarmament,Economic development,  Palestinian conflict, Human rights, Colonialism, and Nuclear weapons and nuclear material:

(Use `help()` to get information and documentation about each dataset).

### Example analysis

Many useful analyses will first involve joining the vote and roll call datasets by the shared `rcid` (roll call ID) column:

```{r joined}

joined = un_votes %>%
  inner_join(un_roll_calls, by = "rcid")

joined
```

One could then count how often each security council country votes "abstention" on a resolution in each year:

```{r by_country_year, dependson = "joined"}
library(lubridate)

by_country_year = joined %>%
  group_by(year = year(date), country) %>%
  summarize(votes = n(),
            percent_ab = mean(vote == "abstain"))

by_country_year
```

After which this can be visualized for one of the security council country or all permanent member countries:

```{r by_country_year_plot, dependson = "by_country_year"}
theme_set(theme_bw())

countries <- c( "China", "France","Russia", "United Kingdom", "United States of America")

# there were fewer votes in 2013
by_country_year %>%
  filter(country %in% countries, year <= 2019) %>%
  ggplot(aes(year, percent_ab, color = country)) +
  geom_line() +
  ylab("% of votes that are 'abstain'")
```

Similarly, we could look at how the voting record of the United States has changed on each of the issues by joining with the `un_roll_call_issues` dataset:

```{r issue_plot, dependson = "joined", fig.height = 6, fig.width = 6}
joined %>%
  filter(country == "China") %>%
  inner_join(un_roll_call_issues, by = "rcid") %>%
  group_by(year = year(date), issue) %>%
  summarize(votes = n(),
            percent_ab = mean(vote == "abstain")) %>%
  filter(votes > 5) %>%
  ggplot(aes(year, percent_ab)) +
  geom_point() +
  geom_smooth(se = FALSE) +
  facet_wrap(~ issue)
```
